Efficiency

### 2017-12-18 DraftExec.Rmd
not finished

---
title: "Efficiency"
author: "Aidan Morrison"
date: "11/12/2017"
output: pdf_document
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

But the most sensitive factor in this relationship is the speed at which the object moves through the liquid.  The drag increases not with the speed ($v$), but with the **square** of the speed . This means if the speed doubles, the drag increases by four.  If the speed triples, the drag increases by a factor of nine.

$$F_D = \frac{1}{2}\rho v^2C_DA$$

@@

The situation becomes much more complicated when the reactor undergoes a sudden change in power output.  If the power is lowered dramatically and suddenly, the production of Xenon continues quite rapidly for some time due to the decay of the large stock of Iodine-135.  With less neutron flux available to 'burn off' the Xenon, the Xenon levels spike, and push down the reactor's reactivity.  Unless the reactor is quickly raised back to relatively high power (~60%) quite quickly (an hour or less), the Xenon levels become so high that the reactor will have to be shut down, otherwise extreme (and dangerous) measures would be required in order to keep the reactor going.  (This is essentially what lead to the Chernobyl Explosion [@WNA2009].)  A fuller discussion of Xenon poisoning can be found in [@garland2005], which demonstrates key concepts related to the poisoning effect shown below.

![Xenon poisoning effect following shutdown from @garland2005](/Users/aidanmorrison/submarines/XenonPoison.png){width=500px}

>>>>

---
title: "Efficiency"
author: "Aidan Morrison"
date: "11/12/2017"
output: bookdown::pdf_document2 
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Figure numbering functions ====

fig <- local({
    i <- 0
    list(
        cap=function(refName, text, center=FALSE, col="black", inline=FALSE) {
            i <<- i + 1
            ref[[refName]] <<- i
            css_ctr <- ""
            if (center) css_ctr <- "text-align:center; display:inline-block; width:100%;"
            cap_txt <- paste0("<span>", text, "</span>")
            anchor <- paste0("<a name=\"", refName, "\"></a>")
            if (inline) {
                paste0(anchor, cap_txt)    
            } else {
                list(anchor=anchor, cap_txt=cap_txt)
            }
        },

        ref=function(refName, link=FALSE, checkRef=TRUE) {

            ## This function puts in a cross reference to a caption. You refer to the
            ## caption with the refName that was passed to fig$cap() (not the code chunk name).
            ## The cross reference can be hyperlinked.

            if (checkRef && !refName %in% names(ref)) stop(paste0("fig$ref() error: ", refName, " not found"))
            if (link) {
                paste0("<A HREF=\"#", refName, "\">Figure ", ref[[refName]], "</A>")
            } else {
                paste0("Figure ", ref[[refName]])
            }
        },

        ref_all=function(){
            ## For debugging
            ref
        })
})

library(knitr)
knit_hooks$set(plot = function(x, options) {
    sty <- ""
    if (options$fig.align == 'default') {
        sty <- ""
    } else {
        sty <- paste0(" style=\"text-align:", options$fig.align, ";\"")
    }

    if (is.list(options$fig.cap)) {
        ## options$fig.cap is a list returned by the function fig$cap()
        str_caption <- options$fig.cap$cap_txt
        str_anchr <- options$fig.cap$anchor
    } else {
        ## options$fig.cap is a character object (hard coded, no anchor)
        str_caption <- options$fig.cap
        str_anchr <- ""
    }

    paste('<figure', sty, '>', str_anchr, '<img src="',
        opts_knit$get('base.url'), paste(x, collapse = '.'),
        '"><figcaption>', str_caption, '</figcaption></figure>',
        sep = '')

})

## This chucnk will read through *this* Rmd file, and attempt to extract all of the 
## labels (not caption text) used for Figure captions. These labels are used
## as anchors, so scanning through the document now will allow us to create cross references
## before the caption actually appears.

## Get the name of this Rmd file
rmdFn <- knitr::current_input()  # filename of input document

## Read lines and close connection
rmdCon <- file(rmdFn, open = "r")
rmdLines <- readLines(rmdCon)
close(rmdCon)

## Pull out all occurences of at least one back tick, followed 
## by any number of characters, followed by fig$cap (all on one line)
figscap_idx <- grep("`+(.*)fig\\$cap", rmdLines)
rmdLines <- rmdLines[figscap_idx]

## Get rid of everything up until the start of the caption label
## This presumes the caption label is the first argument of fig$cap()
## E.g., fig.cap = fig$cap("my_label", ...)
rmdLinesSansPre <- sub("(.*)fig\\$cap(.*?)[\"']", "", rmdLines)

## Identify everything up until the first quote
match_data <- regexpr("(.*?)[\"']", rmdLinesSansPre)

## Reduce the length by one, because we're not interested in the final quote
attr(match_data, "match.length") <- attr(match_data, "match.length") - 1

## Extract
fig_labels <- regmatches(rmdLinesSansPre, match_data, invert=FALSE)

if (length(fig_labels) > 0) {

    ## Test for duplicates
    if (anyDuplicated(fig_labels) > 0) stop("Duplicate caption labels detected")

    ## Create a named list of Figure numbers
    ref <- as.list(1:length(fig_labels))
    names(ref) <- fig_labels
}

```

@@

But the most sensitive factor in this relationship is the speed at which the object moves through the liquid.  The drag increases not with the speed ($v$), but with the **square** of the speed. This means if the speed doubles, the drag increases by four.  If the speed triples, the drag increases by a factor of nine.

$$F_D = \frac{1}{2}\rho v^2C_DA$$
`r fig$cap("xenon1", "Xenon poisoning effect following shutdown from @garland2005")`

@@

The situation becomes much more complicated when the reactor undergoes a sudden change in power output.  If the power is lowered dramatically and suddenly, the production of Xenon continues quite rapidly for some time due to the decay of the large stock of Iodine-135.  With less neutron flux available to 'burn off' the Xenon, the Xenon levels spike, and push down the reactor's reactivity.  Unless the reactor is quickly raised back to relatively high power (~60%) quite quickly (an hour or less), the Xenon levels become so high that the reactor will have to be shut down, otherwise extreme (and dangerous) measures would be required in order to keep the reactor going.  (This is essentially what lead to the Chernobyl Explosion [@WNA2009].)  A fuller discussion of Xenon poisoning can be found in [@garland2005], which demonstrates key concepts related to the poisoning effect shown in `r fig$ref("xenon")`. And you can see that in the [Introduction].

![`r fig$cap("xenon", "Xenon poisoning effect following shutdown from")`](XenonPoison.png){width=500px}

\pagebreak
\begin{figure}
\includegraphics[width=0.9\textwidth]{XenonPoison.png}
\caption{A prototype of the Job Information dialog  @garland2005}
\label{fig:jobInformationDialog}
\end{figure}
